\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-08-02 paper/paper.tex
Add alternative plot for summarizing dms
Work on model assessment section

\subsection{Example 1}
We fit the GLFP model on real hard drive failure data from a cloud-based storage company.  Computer hard drives are known to have a mixture of early and late failures, making the GLFP an appropriate parametric model \cite{chan}.  The data contains the number of hours the hard drive was in operation, and whether the drive failed or was right censored.  No information is available about the cause of failure.  We first focus on the drive brand model with the most observed failures to demonstrate the GLFP model.  We fit the GLFP using a Bayesian framework and specified the following proper priors to ensure a proper posterior distribution.
$$t_{0.5,1} \sim \op{N}(8,4), \quad t_{0.2,2} \sim \op{N}(10,4)$$
$$\mbox{logit}^{-1}\pi_1 \sim \op{Normal}(-3,2),\quad \sigma_1 \sim \op{Lognormal}(0, 2.5), \quad \sigma_2 \sim \op{Lognormal}(0, 2.5) $$

@@

In Figure 1 we plot the Kaplan-Meier adjusted cdf for drive model 14 on Weibull paper.  The solid stepwise curve corresponds to the observed failures.  Censored drives are not plotted.  Standard error bands are calculated using Greenwood's method \cite{green}.  Also plotted is the median of the posterior draws for the GLFP model along with 90\% pointwise credible interval bands.  The non-parametric and parametric model align up quite closely.  Moreover, evidence of at least two failure modes is seen in the acceleration of the hazard rate between 8000 and 20,000 hours.  Therefore, a single Weibull model is clearly not flexible enough to characterize this lifetime distribution.

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{fig/drive14cred.pdf}
  \caption{Estimated GLFP for drive-model 14 plotted on Weibull paper.  Dashed line corresponds to the median of the posterior draws.  Solid blue line is a non-parametric Kaplan-Meier estimator.  Credible 90\% bands are in red.  Greenwood non-parametric error bands are in blue.}
  \label{fig1}
\end{figure}

@@

\section{Data analysis}
\label{sec:Data analysis}
\subsection{Data}
\label{sec:Data}
Backblaze is a company that offers cloud backup storage to protect against data loss.  Since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive-models.  The hard drives continuously spin in controlled storage pods.  Drives are run until failure.  When a hard drive fails it is permanently removed and replaced.  In addition, the number of storage pods is increasing as Backblaze adds to its storage capacity.  Every quarter Backblaze makes its data publicly available through their website \cite{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive-models currently operating.  No other analysis or modeling of the failure data is provided.  Backblaze does, however, encourage others to further analyze its data.

@@

\begin{figure}[H]
  \includegraphics[width=.9\textwidth]{fig/data-sum.pdf}
  \caption{Left: Total number of failures (log scale) for drive-models with at least 3 observed failures in the Backblaze data. Right: Total accumulated time in operation (log scale) for each of the drive-models in the Backblaze data.  The plots are sorted based on the total number of failures on the left.}
  \label{fig1}
\end{figure}

\subsection{Candidate Models}
We considered four models, all based on \ref{eq:hier-model}, which are identified by which model parameters are held constant across drive-models. These are (from most to least restrictive):

@@

\subsection{Prior Distributions}
\label{sec:Prior Distributions}
To complete the full probability model, we need to select prior distributions for the parameters governing the hierarchical model. We select proper priors to ensure a proper posterior.

@@

\subsection{Model Comparisons}
\label{sec:Model Comparisons}
The right side of Figure \ref{fig2} shows that the set of estimated failure curves for all four models that we fit. The upper left panel shows the estimated failure curve fit to all data ignoring drive-model as a factor (Model 1). The upper left plot, which represents Model 2, demonstrates that there is appreciable differentiation between drive-models; note that, because the scale parameter, $\tau_{t_{p2}}$ is learned hierarchically from the data, we can ascertain that there is evidence in the data that this variability is real.

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{fig/heterogeneity-compare-preliminary}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, ordered left to right, top to bottom.}
\label{fig2}
\end{figure}

We can also compare the model fits for each drive-model individually.  Using the set of parameters that maximize the posterior log probability, we examine the GLFP cdf for each of the 4 model specifications.  The GLFP fit for drive-models 2, 9, 14, and 40 are presented in Figure 4.  The black step functions again corresponds to the adjusted non-parametric estimates.  As model complexity increases, the GLFP curves become more flexible and are better able to fit the observed failure data.  All of the GLFP models appear to overestimate the proportion of failed hard drives for drive-model 2, but Model 4 agrees best with the nonparametric estimate.  For drive-model 14, Models 1-3 underestimate the proportion of drives failing, and for drive-model 40, they slightly overestimate the data.  Conversely, Model 4 follows the observed failures quite closely--accurately capturing failures at the lower and upper ends of the distribution.  The difference in accuracy between Models 3 and 4 are and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the fits from Model 3 and 4 line almost exactly on top of each other for drive-model 40.
\begin{figure}[H]
    \centering
   \includegraphics[width=\textwidth]{fig/mod_compare_legend}
		\caption{Estimated GLFP for 4 drive-models plotted on Weibull paper.  The solid step function is the truncated adjusted Kaplan-Meier points.  \label{fig:first}} 
\end{figure}

@@

\subsection{Drive-model Comparisons}
\label{sec:Drive-model Comparisons}
We consider the problem of ranking drive-models. From a
business perspective, it is clear
that we should prefer the drive-models which will provide more years
of service. For ease of exposition, we will assume that the purchase
price of a hard-drive is the same across drive-models.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{fig/b10andpi}
  \caption{Left: 50\% credible intervals for  $t_{0.10}$ (time in years till 10\% of the drives fail). Right: 50\% credible intervals for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of $t_{0.10}$.}
  \label{fig4}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{fig/dm-eval}
  \caption{Left: Posterior predictive relative value-at-loss for new
    unit, by drive-model. Right: TTF (top) and VAF based on 40\% annual depreciation (bottom), for best 11 drive-models.}
  \label{fig5}
\end{figure}

>>>>

\subsection{Example 1}
\label{subsec:ex1}
We fit the GLFP model on real hard drive failure data from a cloud-based storage company.  Computer hard drives are known to have a mixture of early and late failures, making the GLFP an appropriate parametric model \cite{chan}.  The data contains the number of hours the hard drive was in operation, and whether the drive failed or was right censored.  No information is available about the cause of failure.  We first focus on the drive brand model with the most observed failures to demonstrate the GLFP model.  We fit the GLFP using a Bayesian framework and specified the following proper priors to ensure a proper posterior distribution.
$$t_{0.5,1} \sim \op{N}(8,4), \quad t_{0.2,2} \sim \op{N}(10,4)$$
$$\mbox{logit}^{-1}\pi_1 \sim \op{Normal}(-3,2),\quad \sigma_1 \sim \op{Lognormal}(0, 2.5), \quad \sigma_2 \sim \op{Lognormal}(0, 2.5) $$

@@

In Figure 1 we plot the Kaplan-Meier adjusted cdf for drive model 14 on Weibull paper.  The solid stepwise curve corresponds to the observed failures.  Censored drives are not plotted.  Standard error bands are calculated using Greenwood's method \cite{green}.  Also plotted is the median of the posterior draws for the GLFP model along with 90\% pointwise credible interval bands.  The non-parametric and parametric model align up quite closely.  Moreover, evidence of at least two failure modes is seen in the acceleration of the hazard rate between 8000 and 20,000 hours.  Therefore, a single Weibull model is clearly not flexible enough to characterize this lifetime distribution. The discrepancy in the right tail of the distribution appears to be real. We don't provide a solution to this problem here. Certainly, if there are clearly more that two well-separated failure modes, the GLFP will not fit the data well. However, we consider it satisfactory if we can provide a good approximation to the observed lifetime distribution over the bulk of the product life. In practical terms, the right tail is of less importance for electronic goods, due to obsolescence.

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{drive14cred.pdf}
  \caption{Estimated GLFP for drive-model 14 plotted on Weibull paper.  Dashed line corresponds to the median of the posterior draws.  Solid blue line is a non-parametric Kaplan-Meier estimator.  Credible 90\% bands are in red.  Greenwood non-parametric error bands are in blue.}
  \label{fig1}
\end{figure}

@@

\section{Real data analysis}
\label{sec:Data analysis}
\subsection{Backblaze hard drive data}
\label{sec:Data}
Backblaze is a company that offers cloud backup storage to protect against data loss.  Since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive-models.  The hard drives continuously spin in controlled storage pods.  Drives are run until failure.  When a hard drive fails it is permanently removed and replaced.  In addition, the number of storage pods is increasing as Backblaze adds to its storage capacity.  Every quarter Backblaze makes its data publicly available through their website \cite{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive-models currently operating.  No other analysis or modeling of the failure data is provided.  Backblaze does, however, encourage others to further analyze its data.

@@

\begin{figure}[H]
  \includegraphics[width=.9\textwidth]{data-sum.pdf}
  \includegraphics[width=.9\textwidth]{dm-summ-scatter.pdf}
  \caption{Left: Total number of failures (log scale) for drive-models with at least 3 observed failures in the Backblaze data. Right: Total accumulated time in operation (log scale) for each of the drive-models in the Backblaze data.  The plots are sorted based on the total number of failures on the left.}
  \label{fig1}
\end{figure}

\subsection{Modeling}
\subsubsection{Candidate Models}
We considered four models, all based on \ref{eq:hier-model}, which are identified by which model parameters are held constant across drive-models. These are (from most to least restrictive):

@@

\subsubsection{Prior Distributions}
\label{sec:Prior Distributions}
To complete the full probability model, we need to select prior distributions for the parameters governing the hierarchical model. We select proper priors to ensure a proper posterior.

@@

\subsection{Model Selection}
\label{sec:Model Comparisons}
The right side of Figure \ref{fig2} shows that the set of estimated failure curves for all four models that we fit. The upper left panel shows the estimated failure curve fit to all data ignoring drive-model as a factor (Model 1). The upper left plot, which represents Model 2, demonstrates that there is appreciable differentiation between drive-models; note that, because the scale parameter, $\tau_{t_{p2}}$ is learned hierarchically from the data, we can ascertain that there is evidence in the data that this variability is real.

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{heterogeneity-compare-preliminary}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, ordered left to right, top to bottom.}
\label{fig2}
\end{figure}

We can also compare the model fits for each drive-model individually.  Using the set of parameters that maximize the posterior log probability, we examine the GLFP cdf for each of the 4 model specifications.  The GLFP fit for drive-models 2, 9, 14, and 40 are presented in Figure 4.  The black step functions again corresponds to the adjusted non-parametric estimates.  As model complexity increases, the GLFP curves become more flexible and are better able to fit the observed failure data.  All of the GLFP models appear to overestimate the proportion of failed hard drives for drive-model 2, but Model 4 agrees best with the nonparametric estimate.  For drive-model 14, Models 1-3 underestimate the proportion of drives failing, and for drive-model 40, they slightly overestimate the data.  Conversely, Model 4 follows the observed failures quite closely--accurately capturing failures at the lower and upper ends of the distribution.  The difference in accuracy between Models 3 and 4 are and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the fits from Model 3 and 4 line almost exactly on top of each other for drive-model 40.
\begin{figure}[H]
    \centering
   \includegraphics[width=\textwidth]{mod_compare_legend}
		\caption{Estimated GLFP for 4 drive-models plotted on Weibull paper.  The solid step function is the truncated adjusted Kaplan-Meier points.  \label{fig:first}} 
\end{figure}

@@

\subsection{Results}
\subsubsection{Model Assessment}
To assess the goodness of fit, we use a graphical posterior predictive check. As stated by \citet{gelman1996postpred}, a graphical comparison of replicated data sets from the fitted model with the observed data can be very informative with regard to identification of problems with the model.

To generate replicate data sets, we must first decide what to do with regard to censoring and truncation. The representation we choose to display the data, non-parametric probability plots, guides us in making this decision. The variability of this estimator arises primarily from the number of ``at risk" units at any given time, which depends in part on these processes. Since we are not modeling the mechanisms of truncation nor censoring, we want to try to duplicate these mechanisms in the replicated data. Our method for generating replicate a replicate data set $y_{rep,gi}^{(s)}$ is as follows:
\begin{enumerate}
\item Simulate $\tilde{y}_{rep,g,i}^{(s)} \sim \op{GLFP}(\pi^{(s)},\mu_1^{(s)},\sigma_1^{(s)},\mu_{2g}^{(s)}, \sigma_{2g}^{(s)}$
\item If $\tilde{y}_{rep,g,i} < t_{g,i}^L$, then remove this time as this record is not observed
\item Define $m_{g,i}>0$ for each $g$ and $i$. If $c_{g,i}=0$, let $m_{g,i}=\max \{y_{G,i}: G=g\}$, else let $m_{g,i}=y_{g,i}$.\\
If $\tilde{y}_{rep,g,i}^{(s)}>m_{g,i}$, set $y_{rep,g,i}^{(s)}:=m_{g,i},\; c_{rep,g,i}^{(s)}=1$, otherwise set $y_{rep,g,i}^{(s)}=\tilde{y}_{rep,g,i}^{(s)},\; c_{rep,g,i}^{(s)}=0$.
\end{enumerate}

We can compare the realizations of $y_{rep,g}$ to $y_g$ by using them to reestimate the nonparametric estimator. The resulting plots are displayed in figure \ref{post-pred-KM}. For most drive-models, the observed estimates appear to behave similarly to those derived from the replicated data. As discussed in \ref{subsec:ex1}, drive-model 14 has a discrepancy in the right tail, which we addressed there. Drive-moodel 4 also appears as an exception, which we discuss now.

To better understand the reason for the discrepancy between the observed data for drive-model 4 and its posterior predictive distribution, we plot the raw data using a version of the lifetime plot due to WHOM?? along with the truncation-adjusted nonparametric estimate of time to failure and the posterior estimate. The lifetime plot makes it clear that the large discrepancy between the posterior and the nonparametric estimate is driven by a small number of failures (4 or 5) that occur in the first quarter year. Indeed, if we ignore records with observation periods that include the first quarter, the modified nonparametric estimate falls within the posterior 90\% pointwise credible band. Our trouble with fitting this drive-model is that while there is evidence of infant mortality in the relatively few units that were observed in the first quarter, the problem seems to go away much quicker than the early failure mode (shared across drive models) would predict.

Similar plots can help to illustrate the 
and what we call the ``global estimate," corresponding to $\op{GFLP}(\eta_pi, \mu_1,\sigma_1, \eta_{t_2} - \eta_{\sigma_2}\Phi^{-1}(.2), \eta_{\sigma_2})$. These are shown in figure \ref{}.

\begin{figure}
\includegraphics[width=\textwidth,height=.9\textheight]{post-pred-KM-all}
\caption{Nonparametric estimates of proportion failing for each drive-model. Both the original data (\textbf{bold} line) and 19 ``replicated" data sets from the posterior predictive distribution (\textit{dashed} lines) are shown.}
\label{post-pred-KM}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth,height=.9\textheight]{post-pred-KM-all}
\caption{}
\label{mod4}
\end{figure}

\subsubsection{Drive-model Comparisons}
\label{subsubsec:Drive-model Comparisons}
We consider the problem of ranking drive-models. From a
business perspective, it is clear
that we should prefer the drive-models which will provide more years
of service. For ease of exposition, we will assume that the purchase
price of a hard-drive is the same across drive-models.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{b10andpi}
  \caption{Left: 50\% credible intervals for  $t_{0.10}$ (time in years till 10\% of the drives fail). Right: 50\% credible intervals for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of $t_{0.10}$.}
  \label{fig4}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{dm-eval}
  \caption{Left: Posterior predictive relative value-at-loss for new
    unit, by drive-model. Right: TTF (top) and VAF based on 40\% annual depreciation (bottom), for best 11 drive-models.}
  \label{fig5}
\end{figure}
